---
title: "Farms as tasks"
author: "Robert Arbon"
date: "07/05/2019"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(reshape2)
library(RMTL)
library(glmnet)
library(tidyverse)
library(visdat)
library(caret)
set.seed(42)
```

# Introduction

This is an example of using multi-task learning as an alternative to multi-level modelling. CTX-M 
resistance on different farms are treated as separate tasks and a group lasso is placed over the
model to select features which predict resistance across all farms. 

This code is an example of the type of analysis which was performed. Confidentiality requires that the 
real code is not shared. 


# Get data

[REDACTED]

Get the data and remove the unwanted columns. 

```{r}

df<- read_rds(path=paste0(path_to_var, 'pw_ready_for_model.rds'))
df <- filter(df, df$plain_undiluted>0)
df <- select(df, -c(sample_id, visit_number, date_collected, amp_c, ct_pos, cipR, cipro_undiluted, plain_undiluted))
head(df)
```

Remove the missing values and visualise the types: 

```{r}
df <- df[,colSums(is.na(df))==0]
vis_dat(df, sort_type = F)
```

## Separate farms as tasks

Create the design matrix: 

```{r}
farms <- unique(df$farm)
X = list()
Y = list()
for(i in 1:length(farms)){
  tmp <- filter(df, farm==farms[i]) %>%
    select(-farm, -ctx_m)
  dummy <- dummyVars(~ ., data=tmp, fullRank=T)
  x <- predict(dummy, tmp)
  class(x)
  X[[i]] <- matrix(x)
  y <- (df$ctx_m==1)*1
  y[y==0] <- -1
  Y[[i]] <- matrix(y)
  
}
```

Fit the model and select regularization coefficient. 

```{r}
fitr <- MTL(X, Y, type="Classification", Regularization="Lasso", Lam1_seq=10^seq(1,-4, -1),  Lam2=0, opts=list(init=0,  tol=10^-6, maxIter=1500), nfolds=10, stratify=FALSE, parallel=FALSE)
```